---
title: "Loan prediction"
author: "Siva"
date: "September 14, 2017"
output: pdf_document
---

```{r setup}
#Importing Loan Prediction Data
data2=read.csv("/home/siva/Downloads/train1.csv")
#Recoding all categorical variables into 0/1 
data2$Gender=ifelse(data2$Gender=="Male",1,0)
data2$Married=ifelse(data2$Married=="Yes",1,0)
data2$Dependents_1 = ifelse(data2$Dependents == "1",1,0)
data2$Dependents_2 = ifelse(data2$Dependents == "2",1,0)
data2$Dependents_3 = ifelse(data2$Dependents == "3+",1,0)
data2$Education=ifelse(data2$Education=="Graduate",1,0)
data2$Property_Area_1=ifelse(data2$Property_Area=="Urban",1,0)
data2$Property_Area_2=ifelse(data2$Property_Area=="Rural",1,0)
data2$Property_Area_3=ifelse(data2$Property_Area=="Semiurban",1,0)
data2$Self_Employed=ifelse(data2$Self_Employed=="Yes",1,0)
head(data2)
attach(data2)
#fitting a linear model with all variables
model=lm(LoanAmount~Gender+Dependents_1 + Dependents_2+Dependents_3+Self_Employed+Married+ApplicantIncome+CoapplicantIncome+Loan_Amount_Term+Credit_History+Property_Area_1+Property_Area_2+Property_Area_3+Loan_Status,data = data2)

plot(model)
```

```{r cars}
#Summary of the model 
summary(model)
#Summary of forward selection
model_fs_forward=step(model,direction = "forward")
#summary of forward 
summary(model_fs_forward)

plot(model_fs_forward)
```

## forward modelling conclusion 

From this model also the variables Married, Education, ApplicantIncome & Loan_Amount_Term are the significant variables. The total variation explained by the independent
variables on the dependent variable is 37.3% ,i.e., my multiple R-squared value of the model. Since the
p-value is lesser than level of confidence(0.05) it shows the overall model is significant.

```{r pressure}
#performing backward elimination
model_fs_backward=step(model,direction="backward")
#summary of backward elimination 
summary(model_fs_backward)
plot(model_fs_backward)
```

## Backward modelling conclusion 
In this model after eliminating all insignificant variables, the variables Married,Education,ApplicantIncome & Loan_Amount_Term came out to be the most significant variables.The total variation explained by the independent variables on the dependent variable is 80.32%,i.e., my multiple R-squared value of the model.Since the p-value is lesser than level of confidence(0.05) it shows the overall model is significant.


```{r test}

#Performing Stepwise Regression
model_fs_step=step(model,direction="both")
#summary of step model
summary(model_fs_step)
plot(model_fs_step)

```

## Stepwise model conclusion 
In Stepwise Regression model the variables entered in the previous step is been reassessed in each step.After  reassessing all the entered variables,the variables Married, Education, ApplicantIncome & Loan_Amount_Term came out to be the    most significant variables.The total variationexplained by the independent variables on the dependent variable is 80.32%,i.e.,my   multiple R-squared valueof the model.Since the p-value is lesser than level of confidence(0.05) it shows the overall model is significant.

## Result

In this scenario Linear Model has given the most accurate model because the R-Squared Value is the highest amongst all the other models and also the Standard Error is minimum for the Linear Model. Linear Regression Model is most accurate just because we have taken a random independent variable as our dependent variable .

